---
title: GHC Demo Assignment
subtitle: CSC 110- Fall 2025
author: Will Schuckenbrock
date: 10-11-25
format: 
  html:
    toc: true
    toc-depth: 2
    toc-location: body
    theme: cerulean
  pdf:
    toc: true 
    toc-depth: 1 
    fig-width: 8 
    fig-height: 5 
    geometry:
      - top=20mm
      - left=20mm
      - right=20mm
      - heightrounded
---

```{r setup}
#| label: load-packages
#| output: false
#| include: false
library(tidyverse)
```

## Homework

```{r}
#| fig-cap: 
#|   - "Fuel mileage scatterplot"
ggplot(
  mpg, aes(displ, hwy)) +
  geom_point() +
  labs(title='Effects of Engine Displacement on Vehicle Highway MPG', x='Engine displacement (litres)', y='Highway miles per gallon')
```

<https://www.davidson.edu>
  
* Classes
  + Data Science & Society
  + Database Programming
  + Game Development
  + Thesis I/Capstone
  
1. Favorite Shows:
   1. The Boys  
   2. The Terror  
   3. Invincible

Here is a reference[^1]

[^1]: This is the footnote

$$x = \frac{-b \pm \sqrt{b^2- 4ac}}{2a}$$
```{mermaid}
flowchart LR
  A[Road] --> C{Fork}
  C --> D[Left path]
  C --> E[Right path]
```

> Four score and seven years ago our fathers brought forth on this continent, a new nation, conceived in Liberty, and dedicated to the proposition that all men are created equal.

:::{.callout-note}
Im blue.
:::

:::{.callout-tip}
Im green.
:::

:::{.callout-important collapse="true"}
Im red. Close me.
:::

{{< pagebreak >}}

## Reflection

1. **Formatting and Structure**: The final project should be neat and readable, which could get difficult given the number of code blocks, figures, and text that we expect to incorporate. However, HTML's built-in formatting options could help improve the flow of our final product. Options like adding a table of contents with `toc:true` (and all TOC options) or making page breaks and adding dividers will let us customize how our final product is laid out.
2. **Footnotes**: When we finish the final project, I imagine there will be plenty of research backing our datasets, figures, and findings. This research, of course, will constantly be referenced in our writing. Footnotes provide a means of organizing our sources and references in a way more intuitive than in-text citations. Since readers can click-to-follow footnotes, there will be very little confusion on where we got our information for our claims.
3. **Markdown Documentation**: While this isn't really a method, I think having access to the Markdown documentation itself is incredibly helpful. It can act almost like a utility belt when writing in markdown, providing potential solutions to any given problem and giving instructions on how to implement that solution. I can see us using the Quarto Markdown documentation site throughout the project on a regular basis, both for reminders and new ideas.